---
title: "exploration 16th"
format: html
---
##Setting up Libraries
```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(visdat)
library(naniar)
library(janitor)
library(ggformula)
library(dplyr)
library(tinytable)
library(DT)
```
##Reading the data
```{r}
MessyPenguins <- readr::read_delim("Data/Messy_Penguins.csv")%>% 
  janitor::clean_names(case="snake")
```

```{r}
 base::names(MessyPenguins)
dplyr::glimpse(MessyPenguins)
dim(MessyPenguins)
str(MessyPenguins)
```
##Visualising missing data
```{r}
visdat::data_vis_miss(MessyPenguins)
vis_dat(MessyPenguins) + ggtitle(label= "Missing Data in Messy Penguins Dataset", subtitle = "Showing Variable Types")
vis_miss(MessyPenguins) + ggtitle(label = "Missing Data in Messy Penguins Dataset")
```

##Mutate data
```{r}
MessyPenguins_modified2 <- MessyPenguins %>% 
mutate(species = as.factor(species), sex = as.factor(sex), island = as.factor(island)) %>% 
  dplyr::relocate(where(is.factor), .after = species)
MessyPenguins_modified2
tt(MessyPenguins_modified2)

```

##Removing missing data
```{r}
MessyPenguins_modified3 <- MessyPenguins %>% 
naniar::replace_with_na_all(condition =~.x %in% c(" ")) %>% tidyr::drop_na()
MessyPenguins_modified3
```
What can be visualized?
Body mass of penguins throughout the years, species of penguins across islands, sex ratio within species, bill length vs bill depth
##Visualising the data
#Body mass of diff species of Penguins throughout the years

```{r}
MessyPenguins_modified3 %>% 
 gf_bar(year ~ body_mass) %>% 
  gf_labs(x = "Body Mass", y = "Year", title = "Body mass of different species of Penguins throughout the years")

```
#Body mass of diff species and sex of Penguins throughout the years
```{r}
MessyPenguins_modified3 %>% 
 gf_line(year ~ body_mass, color =~ sex) %>% 
  gf_labs(x = "Body Mass", y = "Year", title = "Body mass of different species of Penguins throughout the years")
```


#Species of Penguins across islands
```{r}
MessyPenguins_modified3 %>% 
 gf_point(island ~ species) %>% 
  gf_labs(x = "Species", y = "Island", title = "Species of Penguins across Islands")
```

